---
title: "Oumayma's Questions"
output: html_document
date: "2025-11-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2. Does time of day relate to acceptance?

Variables (Description): time (categorical: 5 levels — morning, afternoon, evening, late night, unknown); acceptance (binary)	

Data Type: Multi-level categorical on binary outcome	

Planned Method of Analysis: One-way ANOVA on mean acceptance rates by time of day	

Hypotheses (H₀ / Hₐ): 
  - H₀: Mean acceptance is the same across all times of day.
  - Hₐ: At least one time-of-day group has a different mean acceptance.

```{r cars}
summary(cars)
```

## 4. Is acceptance different by coupon type?	

Variables (Description): coupon (categorical: 4 levels — bar, coffee house, <$20 restaurant, $20–$50 restaurant); acceptance (binary)

Data Type: Categorical predictor with four levels	One-way ANOVA on acceptance means by coupon category	

Hypotheses (H₀ / Hₐ): 
  - H₀: Mean acceptance is equal across all coupon types.
  - Hₐ: At least one coupon type has a different mean acceptance.

```{r pressure, echo=FALSE}
plot(pressure)
```
